$if(has-frontmatter)$
\frontmatter
$endif$

$if(title)$
\maketitle
\thispagestyle{empty}
$endif$

\newpage

\pagenumbering{Roman}
\setlength{\parskip}{12pt}
%----------------------------------------------
%   Preface
%----------------------------------------------

\raggedright

\Large\textbf{Preface}   

\vspace*{\baselineskip}
\normalsize
\justifying
This thesis aims to explore the first encyclopedia of the ancient world using digital methods within the scope of spatial humanities. Through a combination of skills acquired in the Digital Humanities programme - such as textual analysis, network analysis and data visualisation - and the integration of markup languages for interactive presentations, I have gained valuable training in conducting insightful digital humanities research.

Writing this thesis has been both an enjoyable journey through Pliny's encyclopaedic landscape and a fulfilling exploration of digital methods. Throughout this journey, I deeply appreciate the extensive guidance and help of my supervisor, Professor Margherita Fantoli, and my daily advisor, Laura Soffiantini. Professor Fantoli's constant reminder to ``have fun'' during classes, assignments, events, and feedback sessions encouraged me to tackle challenges and find joy in the process. Discussions with Laura were always enlightening; her inspiring instructions and technical mentorship have been invaluable to my progress.

Last but not least, I would like to thank my dear family and friends for their continuous care, understanding and sweet support.

\newpage


%----------------------------------------------
%   Abstract
%----------------------------------------------

\raggedright

\Large\textbf{Abstract}   

\vspace*{\baselineskip}
\normalsize
\justifying
This study examines Pliny's \textit{Natural History} from a spatial perspective, focusing on the content relating to India and incorporating the digitised and annotated text available in the \href{https://topostext.org/}{TOPOSText project}. The research employs a variety of methodologies, including word frequency and collocation analysis, topic modelling and network analysis, with an integration of close reading practices.
      
The multifaceted role that India plays in the narrative is highlighted in the study’s findings. It emerges not only as a geographical counterpart and repository of precious treasures, but also as an important trading partner of the Roman Empire and the Mediterranean, a context closely related to Pliny’s Stoic perspective on the natural world. In addition, the creation of a network graph linking place and person names associated with India across different books highlights the clustering patterns of different discussion focuses within the content structure.

\newpage

%----------------------------------------------
%   List of abbreviations
%----------------------------------------------

\raggedright

\Large\textbf{List of abbreviations}   

\vspace*{\baselineskip}
\normalsize
API: Application Programming Interface\\
\medskip
CSV: Comma-separated Values\\
\medskip
HTML: HyperText Markup Language\\
\medskip
LDA: Latent Dirichlet Allocation\\
\medskip
NER: Named Entity Recognition\\
\medskip
NLP: Natural Language Processing \\
\medskip
TOPOSText: \href{https://topostext.org/}{TOPOSText project} \\
\medskip
TXT: Text File\\
\medskip
URI: Uniform Resource Identifier\\
\medskip
URL: Uniform Resource Locator\\
\medskip
XML: Extensible Markup Language\\


\newpage

\normalsize
\justifying